---
title: "Outlier Detection"
output: html_notebook
---

## Univariate Method

```{r}
# Method 1
impute_outliers <- function(x,removeNA = TRUE){
  quantiles <- quantile( x, c(.05, .95 ),na.rm = removeNA )
  x[ x < quantiles[1] ] <- mean(x,na.rm = removeNA )
  x[ x > quantiles[2] ] <- median(x,na.rm = removeNA )
  x
}
imputed_data <- impute_outliers(VCOMBCT$CT)
par(mfrow = c(1, 2))
boxplot(VCOMBCT$CT, main="Pressure Height having Outliers", boxwex=0.3)
boxplot(imputed_data, main="Pressure Height with imputed data", boxwex=0.3)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
```{r}
# Method 2 - Boxplot
VCOMBCT <- read.csv(file = 'N:/DaheeKim/Pig_Trial/VCOMBCT.csv')
out <- boxplot.stats(VCOMBCT$CT)$out
out_ind <- which(VCOMBCT$CT %in% c(out))
VCOMBCT[out_ind, ]
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
