---
title: "apply() family"
output:
  html_document:
    toc: true
    toc_float: true
---
* An aggregating function, like for example the mean, or the sum (that return a number or scalar);
* Transforming or subsetting functions; and
* Vectorized functions, which yield more complex structures like lists, vectors, matrices, and arrays.

* Family is made up of the apply(), lapply() , sapply(), vapply(), mapply(), rapply(), and tapply() functions.
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE} 
data(LifeCycleSavings)
data <- LifeCycleSavings
head(data)
str(data)
```
Function  | Argument | Input | Output
------------- | ------------- | ------------- | ------------- |
apply | apply(x, MARGIN, FUN) | Data frame or matrix | vector, list, array
lapply | 	lapply(X, FUN) | 	List, vector or data frame | 	List
sapply | 	sapply(X, FUN) | 	List, vector or data frame | 	vector or matrix

###apply()
* Returns a vector or array or list of values obtained by applying a function to margins of an array or matrix.

apply(X,Margin,Fun)
FUN: R function ,also includes a User Defined Function ex)sum, mean, max, min, median, var..
```{r}
head(data)
apply(data,2,mean) #column mean
apply(data,1,mean) #row mean
head(apply(data,1:2, function(x) x/2),5) #UDF
```

###lapply()
* lapply returns a list of the same length as X, each element of which is the result of applying FUN to the corresponding element of X.
* Used for comparisons or aggregations from different dataframes.
```{r ,fig.width=2}
##Install packages
using<-function(...) {
  libs<-unlist(list(...))
  req<-unlist(lapply(libs,require,character.only=TRUE))
  need<-libs[req==FALSE]
  if(length(need)>0){ 
    install.packages(need)
    lapply(need,require,character.only=TRUE)
  }
}
using("knitr","dplyr","kableExtra")

A<- cars
B<- women
C<- rock
dataset_list <- list(A,B,C)
lapply(dataset_list,"[",,2)#extract 2nd column from multiple dataframe
kable(lapply(dataset_list,"[",1,)) %>% #extract 1st row from multiple dataframe
    kable_styling(bootstrap_options = c("striped", "hover")) 
lapply(dataset_list,"[",1,2) # extract 1st row, 2nd column value

second <- lapply(dataset_list,"[",,2) #mean of each 2nd column
avg <-lapply(second,mean)
avg
class(avg) # "list""
```

###sapply()
* sapply is a user-friendly version of lapply by default returning a vector or matrix if appropriate.
```{r fig.width=2}
#version1
dataset_list <- list(A[,1],B[,1],C[,1])
avg <- sapply(dataset_list, mean)
avg 
class(avg) #"numeric"

#version2
avg <- function(x) {  
  ( min(x) + max(x) ) / 2}
avg2 <- sapply(dataset_list, avg)
avg2
```

###tapply()
* Apply a function to each cell of a ragged array, that is to each (non-empty) group of values given by a unique combination of the levels of certain factors.
```{r}
#mean by group
tapply(data$sr,rownames(data), mean)
```


