---
title: "Churn Prediction"
author:DaheeKim

output: html_notebook
---

In an increasing fragmented market, creating and maintaining our loyal customer is an essntial problem. Based on the customer behavior, transanction, we will predict customer segments and create model to find the pattern.

#Load data from github
```{r}
library(readr)
test = "https://raw.githubusercontent.com/dana6691/R_project/master/churnTrain.csv"
train = "https://raw.githubusercontent.com/dana6691/R_project/master/churnTrain.csv"
test<-read_csv(url(test))
train<-read_csv(url(train))
```

```{r}
train$Area_Code <- as.character(train$Area_Code)
train$No_CS_Calls <- as.character(train$No_CS_Calls)
#Change logic to numerical  
train$Churn[train$Churn == "FALSE"] <- 0
train$Churn[train$Churn == "TRUE"] <- 1
library(dplyr)
str(train)
```
- Categorical features: State, International_Plan, Voice_Mail_Plan,  Area_Code,No_CS_Calls

- Numerical features:Account_Length,No_Vmail_Messages,Total_Day_minutes,Total_Day_Calls,Total_Day_charge,Total_Eve_Minutes,Total_Eve_Calls,Total_Eve_Charge,Total_Night_Minutes,Total_Night_Calls,Total_Night_Charge,Total_Intl_Minutes,Total_Intl_Charge,Churn
```{r echo=FALSE}
library(skimr)
skim(train)
```

#Categorical Features Plot
```{r}
library(dplyr)
mytable <- xtabs(~ State+Churn, data=train)
state <- as.data.frame(prop.table(mytable, 1)) # row proportions
mytable <- xtabs(~ International_Plan+Churn, data=train)
International_Plan <- as.data.frame(prop.table(mytable, 1)) # row proportions
mytable <- xtabs(~ Voice_Mail_Plan+Churn, data=train)
Voice_Mail_Plan <- as.data.frame(prop.table(mytable, 1)) # row proportions
mytable <- xtabs(~ Area_Code+Churn, data=train)
Area_Code <- as.data.frame(prop.table(mytable, 1)) # row proportions
mytable <- xtabs(~ No_CS_Calls+Churn, data=train)
No_CS_Calls <- as.data.frame(prop.table(mytable, 1)) # row proportions
table(train$Churn, train$State)

library(ggplot2)
ggplot(data=subset(state, Churn==0),aes(x=State, y=Freq,fill=State))+
  geom_bar(position="stack", stat="identity") + ylab("Retention Rate") + theme(legend.position = "none")
a2 <-ggplot(data=subset(International_Plan, Churn==0),aes(x=International_Plan, y=Freq,fill=International_Plan))+
  geom_bar(position="stack", stat="identity") + ylab("Retention Rate")+ theme(legend.position = "none")
a3 <-ggplot(data=subset(Voice_Mail_Plan, Churn==0),aes(x=Voice_Mail_Plan, y=Freq,fill=Voice_Mail_Plan))+
  geom_bar(position="stack", stat="identity") + ylab("Retention Rate")+ theme(legend.position = "none")
a4 <-ggplot(data=subset(Area_Code, Churn==0),aes(x=Area_Code, y=Freq,fill=Area_Code))+
  geom_bar(position="stack", stat="identity") + ylab("Retention Rate")+ theme(legend.position = "none")
a5 <-ggplot(data=subset(No_CS_Calls, Churn==0),aes(x=No_CS_Calls, y=Freq,fill=No_CS_Calls))+
  geom_bar(position="stack", stat="identity") + ylab("Retention Rate")+ theme(legend.position = "none")
library(ggpubr)
ggarrange(a2,a3,a4,a5,ncol =2, nrow = 2)

```


#Categorical Features Plot
```{r}
mytable <- xtabs(~ Account_Length+Churn, data=train)
Account_Length <- as.data.frame(prop.table(mytable, 1)) # row proportions
subset(Account_Length, Churn==0)
Account_Length$Account_Length <- as.numeric(Account_Length$Account_Length)
ggplot()+
  geom_line(data=subset(Account_Length, Churn==0),aes(x=Account_Length, y=Freq,group=1)) + ylab("Retention Rate") + theme(legend.position = "none") + scale_x_continuous(name = "Account Length", breaks=seq(0,max(Account_Length$Account_Length),10))
mytable <- xtabs(~ Account_Length+Churn, data=train)
Account_Length <- as.data.frame(prop.table(mytable, 1)) # row proportions
ggplot()+
  geom_line(data=subset(No_Vmail_Messages, Churn==0),aes(x=Account_Length, y=Freq,group=1)) + ylab("Retention Rate") + theme(legend.position = "none") + scale_x_continuous(name = "Account Length", breaks=seq(0,max(Account_Length$Account_Length),10))
ggplot()+
  geom_line(data=subset(Account_Length, Churn==0),aes(x=Account_Length, y=Freq,group=1)) + ylab("Retention Rate") + theme(legend.position = "none") + scale_x_continuous(name = "Account Length", breaks=seq(0,max(Account_Length$Account_Length),10))

```
Account_Length,No_Vmail_Messages,Total_Day_minutes,Total_Day_Calls,Total_Day_charge,Total_Eve_Minutes,Total_Eve_Calls,Total_Eve_Charge,Total_Night_Minutes,Total_Night_Calls,Total_Night_Charge,Total_Intl_Minutes,Total_Intl_Charge,Churn
