---
title: "Correlation Analysis"
output: github_document
---

###  Correlation between 2 variables
```{r}
# Pearson correlation between 2 variables
library(readxl)
data <- read_excel("~/VScode_project/R_projects/Data/TSCW200102.xlsx")
data <- data[, c(10,13,14,18,19)]
cor(data$ADG, data$FCR) # “pearson”
cor(data$ADG, data$FCR, method = "spearman")
cor(data$ADG, data$FCR, method = "kendall")
```
- **Pearson correlation** is often used for quantitative continuous variables that have a linear relationship
- **Spearman correlation** which is actually similar to Pearson but based on the ranked values for each variable rather than on the raw data, is often used to evaluate relationships involving qualitative ordinal variables or quantitative variables if the link is partially linear
- **Kendall** which is computed from the number of concordant and discordant pairs is often used for qualitative ordinal variables

Hypothesis

- H0: ρ=0 (there is no linear relationship between the two variables)
- H1: ρ≠0 (there is a linear relationship between the two variables)

### Correlation for all variables
```{r}
library(GGally)
ggpairs(data)
# plot(data)
# ggpairs(data, columns = c(15,82:87), ggplot2::aes(colour=Crop, na.rm = TRUE))
```

### 1. Pearson correlation test Correlogram
```{r fig.height=6, fig.width=6}
library(corrplot)
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],method="pearson")
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(data)
M1 <- cor(data, method="pearson")
corrplot(M1,  type="upper", order="hclust", # addCoef.col = "black",
         tl.col="black", tl.srt=45, 
         p.mat = p.mat, sig.level = 0.05)
```

#### Method 2 - with p-value
- method: number, circle, square, ellipse, color, pie
- type: full, lower, upper
- addCoef.col: color of correlation coefficient
- insig: pch, p-value, black, n
- tl.col: variable name color
- tl.pos: position of text labels. lt, ld, td, d, n

```{r}
library(corrplot)
library(Hmisc)
res <- rcorr(as.matrix(data), type = "pearson") # spearman, pearson
corrplot(res$r, type="upper", method="circle",p.mat = res$P, sig.level = 0.05,
         tl.col = "black",addCoef.col = 'grey50')
```

#### Method 3 - without p-value
```{r}
# pearson, spearman, kendall
M <- cor(data, method="pearson", use="pairwise.complete.obs")
corrplot(M, type = "upper", tl.col = "black",addCoef.col = 'grey50')
```

#### Method 4
```{r echo=FALSE, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, paged.print=FALSE}
library(reshape2)
library(ggpubr)
dtmelt<- melt(data,measure = c("ADG", "FCR"))
ggscatter(dtmelt, x = "Survival", y = "value", color="variable",palette = c("#FC4E07", "palegreen4","#E7B800") ,
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "FG", ylab = "", title="MGR/CF vs F:G") + 
          facet_grid(variable~., scales = "free")+  
          theme(legend.position = "none")
```

#### Method 5
```{r fig.height=4, fig.width=4, message=FALSE, warning=FALSE, paged.print=FALSE}
library("PerformanceAnalytics")
chart.Correlation(data, histogram=TRUE, pch=19)
```

#### Method 6
```{r fig.height=4, fig.width=4, message=FALSE, warning=FALSE, paged.print=FALSE}
plot(data)
```

#### Method 7. Correlation Network Plot
```{r fig.height=6, fig.width=6, warning=FALSE}
library(corrr) 
library(dplyr)
mydata <- data[,c(77:79,82:87)] # remove BiCarb_P,N
res.cor <- correlate(mydata,use = "pairwise.complete.obs", method = "pearson") # "pearson", "kendall", "spearman"
res.cor %>% rplot()
res.cor %>%
  mutate_if(is.numeric, coalesce, 0) %>% # replace NA to 0
  network_plot(min_cor = .6)
```

### 2.Spearman’s rho correlation test
statistic is also used to estimate a rank-based measure of association. This test may be used if the data do not come from a bivariate normal distribution.
```{r fig.height=6, fig.width=6, warning=FALSE}
library(corrplot)
M1 <- cor(data)
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],method = "spearman")
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(data)
M1 <- cor(data, method="spearman")
corrplot(M1,  type="upper", order="hclust", # addCoef.col = "black",
         tl.col="black", tl.srt=45, 
         p.mat = p.mat, sig.level = 0.05)
```

### 3.Kendall's tau correlation test
used to estimate a rank-based measure of association. This test may be used if the data do not necessarily come from a bivariate normal distribution.
```{r fig.height=6, fig.width=6}
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],method="kendall")
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(data)
M1 <- cor(data, method="kendall")
corrplot(M1,  type="upper", order="hclust", addCoef.col = "black", 
         tl.col="black", tl.srt=20, 
         p.mat = p.mat, sig.level = 0.05)
```

```{r fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
library(rstatix)
cor.mat <- 
  cor_mat(
  data,
  vars = NULL,
  method = "pearson", #"kendall", or "spearman"
  alternative = "two.sided",
  conf.level = 0.95)
cor.mat %>%
  cor_reorder() %>%
  pull_upper_triangle() %>%
  cor_plot(label = TRUE)

# cor.mat %>% cor_get_pval() # Significance levels 
# cor.mat %>% cor_gather() # Gather/collapse correlation matrix into long format
```

### Heatmap
```{r}
M <- cor(data)
heatmap(M)
```


