---
title: "Easy EDA with *DataExplorer* package"
author: Dahee Kim
date: January 5, 2020
output:
  github_document:
    toc: true
    toc_depth: 3
# output:
#   html_document:
#     theme: lumen
#     toc: true
#     toc_float: true
#     number_sections: true
---

```{r include=FALSE}
library(prettydoc)
library(DataExplorer)
library(readr)
library(ggplot2)
#import data
dt= read_csv('https://raw.githubusercontent.com/dana6691/R_project/master/Data/insurance.csv', col_names = TRUE)
dt <- as.data.frame(dt)
str(dt)
```

## Easy Data Profiling Report
To get a report for the insurance dataset with response variable bmi, `create_report(dataname)`
```{r}
#create_report(dt, y = "bmi")
```
- Basic Statistics
    - Raw Counts
    - Percentages
- Data Structure
- Missing Data Profile
- Univariate Distribution
    - Histogram
    - Bar Chart (by frequency)
    - Bar Chart (by bmi)
    - QQ Plot
    - QQ Plot (by bmi)
- Correlation Analysis
- Principal Component Analysis
- Bivariate Distribution
    - Boxplot (by bmi)
    - Scatterplot (by bmi)
    
## Structure of data
```{r}
data_list <- list(dt)
plot_str(data_list)
```

## Variable information
```{r}
plot_intro(dt)
```

## Missing Data by features
```{r}
plot_missing(dt)
```

## Continuous Variable
### Histogram for Continuous Variables
```{r}
plot_histogram(dt)
```

### Scatterplot `bmi` with all other continuous features
```{r}
plot_scatterplot(split_columns(dt)$continuous, by = "bmi")
```

### QQ plot of all continuous variables
```{r}
plot_qq(dt)
plot_qq(dt, by = "bmi",theme_config = list("aspect.ratio" = 1))
```

### Density estimates for each continuous features
```{r}
plot_density(dt,theme_config = list(
  "aspect.ratio" = 1
))
```

## Categorical Variable
### Categorical Data - Frequency Table
```{r}
plot_bar(dt)
```

### Boxplot by Categorical Variables
```{r}
plot_boxplot(dt, by= 'sex',  ncol = 2)
plot_boxplot(dt, by= 'smoker',  ncol = 2)
plot_boxplot(dt, by= 'region',  ncol = 2)
```

## Correlation Analysis
```{r}
plot_correlation(dt)
```

## Visualize principle component analysis
```{r}
plot_prcomp(dt)
```

## Feature Engineering
```{r}
#Dummify diamonds dataset
head(dummify(dt))

#Update columns
head(update_columns(dt, c("sex", "smoker","region"), as.factor))

#Drop columns
head(drop_columns(dt, 1:2),5)
```


