---
title: "Data Visualization"
author: "Dahee Kim"
date: "March 3, 2019"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true
    theme: united  # many options for theme, this one is my favorite.
---
#Data Source:
[linked](https://archive.ics.uci.edu/ml/datasets/Mice+Protein+Expression)

#Data Set Information:

The data set consists of the expression levels of 77 proteins/protein modifications that produced detectable signals in the nuclear fraction of cortex. There are 38 control mice and 34 trisomic mice (Down syndrome), for a total of 72 mice. In the experiments, 15 measurements were registered of each protein per sample/mouse. Therefore, for control mice, there are 38x15, or 570 measurements, and for trisomic mice, there are 34x15, or 510 measurements. The dataset contains a total of 1080 measurements per protein. Each measurement can be considered as an independent sample/mouse. 

The eight classes of mice are described based on features such as genotype, behavior and treatment. According to genotype, mice can be control or trisomic. According to behavior, some mice have been stimulated to learn (context-shock) and others have not (shock-context) and in order to assess the effect of the drug memantine in recovering the ability to learn in trisomic mice, some mice have been injected with the drug and others have not. 

Classes: 

* c-CS-s: control mice, stimulated to learn, injected with saline (9 mice) 
* c-CS-m: control mice, stimulated to learn, injected with memantine (10 mice) 
* c-SC-s: control mice, not stimulated to learn, injected with saline (9 mice) 
* c-SC-m: control mice, not stimulated to learn, injected with memantine (10 mice) 

* t-CS-s: trisomy mice, stimulated to learn, injected with saline (7 mice) 
* t-CS-m: trisomy mice, stimulated to learn, injected with memantine (9 mice) 
* t-SC-s: trisomy mice, not stimulated to learn, injected with saline (9 mice) 
* t-SC-m: trisomy mice, not stimulated to learn, injected with memantine (9 mice) 

#Attribute Information:

1. Mouse ID 
2.  Values of expression levels of 77 proteins; indicating that they were measured in the nuclear fraction. For example: DYRK1A_n 
79. Genotype: control (c) or trisomy (t) 
80. Treatment type: memantine (m) or saline (s) 
81. Behavior: context-shock (CS) or shock-context (SC) 
82. Class: c-CS-s, c-CS-m, c-SC-s, c-SC-m, t-CS-s, t-CS-m, t-SC-s, t-SC-m 
```{r message=FALSE, warning=FALSE}
library(readxl)
data <- read_excel("Data_Cortex_Nuclear.xlsx")
head(data)
```

##Scatter plot
```{r fig.width=7, fig.height=5,error=FALSE, message=FALSE, warning=FALSE}
#Categorical independent variable
library(gridExtra)
library(ggplot2)  
a<- ggplot(data, aes(x=Treatment,y=ITSN1_N))+
  geom_point(aes(color=Behavior))+
  facet_wrap(~Genotype)+
  scale_fill_brewer() +
  theme(legend.position = c(0.85, 0.8))

#Continuous variables
b<- ggplot(data, aes(BDNF_N, ITSN1_N)) + 
  geom_point(aes(color = Behavior)) + 
  theme_bw()+
  labs(title="Scatterplot")+
  theme(legend.position = c(0.2, 0.8))

grid.arrange(a,b, ncol=2,nrow=1)

ggplot(data, aes(ELK_N, ERK_N)) + 
  geom_point(aes(color = class..82)) + 
  theme_bw()+
  scale_colour_brewer(palette = "Set2")+
  facet_wrap(~class..82)
```

##Correlation Matrix - first 10 protein
```{r fig.width=5, fig.height=5,error=FALSE, message=FALSE, warning=FALSE}
library(corrplot)
data1 <- data[,c(3:12)]
data1 <- na.omit(data1)
names(data1)

M1 <- cor(data1)
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(mtcars)
corrplot(M1,  type="upper", order="hclust",tl.col="black", tl.srt=45, p.mat = p.mat, sig.level = 0.01)
corrplot(M1, method="color",  
         type="upper", order="hclust", 
         addCoef.col = "black", 
         tl.col="black", tl.srt=45,
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         diag=FALSE 
         )
plot(data1)
```

##Correlogram
```{r,fig.width=5, fig.height=5, message=FALSE, error=FALSE}
library(corrgram)
data1 <- data[,60:82]
corrgram(data1, order=NULL, panel=panel.shade, text.panel=panel.txt,
           main="Correlogram") 
```

##Boxplot
```{r error=FALSE, message=FALSE, warning=FALSE}
library(reshape2)
library(ggplot2)
library(plotly)
library(ggthemes) #custom theme background
#using ggplot
g <- ggplot(data, aes(class..82,ITSN1_N,fill=class..82)) 
g +  geom_boxplot()+
  scale_y_continuous("ITSN1_N", breaks= seq(0,15000, by=500))+
  labs(title="Box plot", 
       subtitle="ITSN1_N gene grouped by Treatment",
       caption="Source: mpg",
       x="Treatment",
       y="ITSN1_N") +
  guides(fill=guide_legend("Treatment"))+ 
  theme_stata() + #background theme
  scale_color_stata() + #background theme
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) 

#plot_ly
data2 <- data[,c(70:77,79,80,81,82)]
df <- melt(data2,id=c("Genotype","Behavior","class..82","Treatment" ))
plot_ly(df, x = ~variable, y = ~value, color = ~Genotype,type = "box", colors = "Set3")%>% 
         layout(boxmode = "group",
                xaxis = list(title=''), 
                yaxis = list(title='Value'))

```

##Violin plot
```{r}
#violin
g+ geom_violin(aes(fill=factor(Behavior))) +
  labs(title="Violin plot") +
  guides(fill=guide_legend("Behavior"))+ 
   theme_economist() + 
  scale_color_economist()+
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="darkblue"))
```

##Dendrogram plot
```{r error=FALSE, message=FALSE, warning=FALSE}
library(dplyr) #for dataset manipulation
library(knitr) #for neaty dataset printing
library(car)
data2 <- na.omit(data)
dfdf1<-data %>% group_by(class..82) %>%
 summarise_at(vars(pMTOR_N:pGSK3B_N),mean, na.rm=TRUE)
dfdf2<-data %>% group_by(class..82) %>%
 summarise_at(vars(pMTOR_N:pGSK3B_N),mean, na.rm=TRUE) %>%
 filter(class..82 %in% c("c-CS-m"))
dfdf2t <- t(dfdf2)
names <- rownames(dfdf2t)
dfdf3 <- cbind(names,dfdf2t)
dfdf3 <- dfdf3[-1,]
rownames(dfdf3) <- NULL
colnames(dfdf3) <- c("protein","mean")
kable(dfdf3)

means <- dfdf3[,2]
d_mean <- dist(means, method = "euclidean")
fit <- hclust(d_mean)
h <- 2
groups <- cutree(fit, h = h)
plot(fit, labels = dfdf3[,1], main = "Dendrogram")
```

##Chord-diagrams
```{r error=FALSE, message=FALSE, warning=FALSE}
library(circlize) #for chord-diagrams
dfdf11<-data %>% group_by(class..82) %>%
 summarise_at(vars(APP_N:MTOR_N),mean, na.rm=TRUE)
dfdf11 <- as.data.frame(dfdf11)
rownames(dfdf11) <- dfdf11[,1]
dfdf11 <- dfdf11[,-1]
chordDiagram(dfdf11)
```

##Radar Plot
```{r, message=FALSE, error=FALSE}
par(mfrow=c(1,2))
#Empty inside
library(fmsb)
dfdf22<-data %>% group_by(class..82) %>%
 summarise_at(vars(pMTOR_N:pGSK3B_N),mean, na.rm=TRUE) %>%
 filter(class..82 %in% c("t-CS-s"))
dfdf22<- dfdf22[,-1]

dfdf23<-data %>% group_by(class..82) %>%
 summarise_at(vars(pMTOR_N:pGSK3B_N),mean, na.rm=TRUE) %>%
 filter(class..82 %in% c("t-CS-m"))
dfdf23<- dfdf23[,-1]
maxdf <- rep(1,12)
mindf <- rep(0,12)
dfdf3<- data.frame(rbind(maxdf,mindf,dfdf22,dfdf23))
radarchart(dfdf3)


#Fill in
dfdf24<-data %>% group_by(class..82) %>%
 summarise_at(vars(pMTOR_N:pGSK3B_N),mean, na.rm=TRUE) 
dfdf24 <- data.frame(t(dfdf24))
#firt row as column name
rownames(dfdf24[1,]) <- NULL
colnames(dfdf24) <- as.character(unlist(dfdf24[1,])) 
dfdf24 = dfdf24[-1, ]
#factor to numeric - all variables
con.names = dfdf24 %>% select_if(is.factor) %>% colnames()
dfdf24[,con.names] = lapply(dfdf24[,con.names], as.character)
can.names = dfdf24 %>% select_if(is.character) %>% colnames()
dfdf24[,can.names] = lapply(dfdf24[,can.names], as.numeric)


dfdf1 <- dfdf24[1,]
dfdf2 <- dfdf24[2,]
dfdf3 <- dfdf24[3,]
comparedf <- rbind(maxdf,mindf,dfdf1,dfdf2,dfdf3)
radarchart(comparedf)


colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )
radarchart( comparedf  , axistype=1 , 
    #custom polygon
    pcol=colors_border, pfcol=colors_in, plwd=2 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
    #custom labels
    vlcex=0.8 
    )
legend(x=1.5, y=1, legend = rownames(comparedf[-c(1,2),]), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1.2, pt.cex=3)
 
```

##ggplot2
```{r error=FALSE, message=FALSE, warning=FALSE}
library(dplyr) #for dataset manipulation
library(reshape2)
library(knitr) #for neaty dataset printing
library(ggplot2)
data2 <- data[,58:82]
df <- melt(data2,id=c("Genotype","Treatment","Behavior","class..82" ))
ggplot(df, aes(x=variable,y=value,group=Genotype)) + 
  geom_point(aes(color=Genotype),size=0.5,shape=3)+
  scale_colour_brewer(palette = "Set1") +
  theme_economist() + 
  scale_color_economist() +
  theme(axis.text.x = element_text(angle=65, vjust=0.6))+
  theme(legend.background = element_rect( fill = 'grey95', size = 0.3, linetype='solid',colour ="darkblue"))+
  theme(legend.title = element_text(face="bold"))


#facet_wrap
df <- na.omit(df)
mean_df<-df %>% group_by(class..82,Genotype,variable) %>%
 summarise(mean=mean(value)) 

p <- ggplot(mean_df, aes(x=variable,y = mean,fill=class..82)) +
  geom_bar(position="dodge", stat="identity")+
  facet_wrap(~Genotype) +
  guides(fill=guide_legend("Treatment"))
p + 
  scale_fill_brewer(palette = "Spectral") + 
  coord_flip()

#facet_grid
df <- na.omit(df)
mean_df2 <-df %>% group_by(class..82,Behavior,variable) %>%
 summarise(mean=mean(value)) 

p1 <- ggplot(mean_df2, aes(x=variable,y = mean,fill=class..82)) +
  geom_bar(position="dodge", stat="identity")+
  facet_grid(Behavior~.) +
  guides(fill=guide_legend("Treatment"))
p1 + scale_fill_brewer(palette = "PuBu") +theme_dark() +theme(axis.text.x = element_text(angle=65, vjust=0.6)) 


#Multiple variables mean
#data1 <- na.omit(data)
#dfdf<-data1 %>% group_by(class..82) %>%
#  summarise_at(vars(Bcatenin_N:MTOR_N),mean, na.rm=TRUE)
#dfdf2<- melt(dfdf)
#kable(dfdf2)
```

##Color
```{r echo=FALSE, error=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
library(png)
library(grid)
img <- readPNG("color1.png")
 grid.raster(img)
#display.brewer.all()
```

##Plotly
```{r error=FALSE, message=FALSE, warning=FALSE}
#Linear
plot_ly(data=mean_df2, x=~variable,y=~mean,color=~class..82,type = 'scatter', mode = 'lines') 


#Scatter
plot_ly(data=data,x=~Tau_N, y=~ERK_N,
        marker = list(size = 5,
                       color = 'rgba(255, 182, 193, .9)',
                       line = list(color = 'rgba(152, 0, 0, .8)',
                                   width = 1))) %>%
  group_by(class..82) %>%
  layout(title = 'Styled Scatter')


x <- c(1:1080)
x1<- rep(1:180,6)
data2<- cbind(data,x1)

#smoothing line
ggplot(data2, aes(x=x1, y=SOD1_N,color=class..82)) + 
  geom_point(size=1) +
  geom_smooth(position = "identity")

#line + scatter
plot_ly(data2, x = ~x1, y = ~pNR2B_N, type = 'scatter',color=~class..82,mode = 'lines')

p <- plot_ly(data, x = ~x, y = ~pNR2B_N) 
add_markers(p, linetype = ~Behavior)


```

##Lollipop
```{r, message=FALSE, error=FALSE}
# Lillopop Plot
ggplot(mean_df2, aes(x=variable, y=mean)) + 
  geom_point(color="orange",size=4) + 
  geom_segment(aes(x=variable, xend=variable, y=0.5, yend=mean),color='grey') + 
  theme( panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_text(angle=65, vjust=0.6))+ 
  labs(title="Lollipop Chart", subtitle="Treatment") 
```

##Density plot
```{r, message=FALSE, error=FALSE}
theme_set(theme_classic())

g <- ggplot(data, aes(pGSK3B_Tyr216_N))
g + geom_density(aes(fill=factor(class..82)), alpha=0.8) + 
    labs(title="Density plot", 
         subtitle="pGSK3B_Tyr216_N Grouped by classs",
         caption="Source: ",
         x="pGSK3B_Tyr216_N",
         fill="#class") +
    facet_wrap(~Behavior)
```


