---
title: "Table Display"
author: Dahee Kim
output: github_document
always_allow_html: true
---
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#theme style 
#sandstone, united, journalm flatly, darkly, cyborg, cosmo, cerulean, LUX, Literam, Lumen, minty, pulse, materia, sketchy, simplex. spacelab, solar, slate, yeti, superhero
#"default", "cerulean", "journal", "flatly", "darkly", "readable", "spacelab", "united", "cosmo", "lumen", "paper", "sandstone", "simplex", "yeti"
# https://bootswatch.com/
#https://holtzy.github.io/Pimp-my-rmd/  #sososososoos

```
\begin{shaded}
Red text with a gray background.
\end{shaded}


```{r results = 'asis', global_options, include=FALSE}
#global options
knitr::opts_chunk$set( warning=FALSE, message=FALSE)
```

### kable
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
**kable**(x, format, digits = getOption("digits"), row.names = NA, col.names = NA, align, 
    caption = NULL, label = NULL, format.args = list(), escape = TRUE, ...)
</div>
------------------------------------------------------------------------------------------
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>

<div class = "blue">
The function *kable* is a simple table generator, from library `knitr` 

* digits: number of digits for individual columns
* align: 'l'(left), 'c'(center),'r'(right) ex) c('c','l','c')
* caption
* label

</div>

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::kable(head(mtcars), digits = 2)
```

### DT
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
**datatable**(data, options = list(), class = "display", callback = JS("return table;"), 
    rownames, colnames, container, caption = NULL, filter = c("none", 
        "bottom", "top"), escape = TRUE, style = "default", width = NULL, 
    height = NULL, elementId = NULL, fillContainer = getOption("DT.fillContainer", 
        NULL), autoHideNavigation = getOption("DT.autoHideNavigation", 
        NULL), selection = c("multiple", "single", "none"), extensions = list(), 
    plugins = NULL, editable = FALSE)
</div>
------------------------------------------------------------------------------------------
<div class = "blue">
* caption
* filter: add filter to each column
* editable: TRUE/FALSE
* colnames: colnames = c('Here', 'Are', 'Some', 'New', 'Names') colnames = c('A Better Name' = 'Sepal.Width') colnames = c('Another Better Name' = 2, 'Yet Another Name' = 4
* pageLength(options): limited showing row  c("none", "bottom", "top")
* scrollX(options): get vertical scroll bar
</div>
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(DT)
longley <- data.frame(longley)
datatable(head(longley), rownames = FALSE, filter="top", options = list(pageLength = 6, scrollX=T) )
```

### tibble
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>

<div class = "blue">
**tibble**(..., .rows = NULL, .name_repair = c("check_unique", "unique",
  "universal", "minimal"))
</div>
--------------------------------------------------------------------------------------------
<div class = "blue">
* Re-imagining of the data.frame
* tibble() never changes the type of the inputs,never changes the names of variables, easier than data.frame()
</div>
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tibble)
as_tibble(longley)
tibble(longley$GNP, longley$Unemployed, total = longley$GNP + longley$Unemployed)
```

### xtable
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
**xtable**(x, caption = NULL, label = NULL, align = NULL, digits = NULL,
display = NULL, auto = FALSE, ...)
</div>
```{r xtable, fig.height=10, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
library(xtable)
f1 <- aov(Year ~ GNP + Unemployed +  Population, data = longley) #latex input
xtable(f1)
```

### expss
<div class = "blue">
*expss* provides tabulation functions with support for 'SPSS'-style labels, multiple / nested banners, weights, multiple-response variables and significance testing
</div>
```{r fig.height=10, fig.width=10}
library(expss)
mtcars = apply_labels(mtcars,
                      mpg = "Miles/(US) gallon",
                      cyl = "Number of cylinders",
                      disp = "Displacement (cu.in.)",
                      hp = "Gross horsepower",
                      drat = "Rear axle ratio",
                      wt = "Weight (1000 lbs)",
                      qsec = "1/4 mile time",
                      vs = "Engine",
                      vs = c("V-engine" = 0,
                             "Straight engine" = 1),
                      am = "Transmission",
                      am = c("Automatic" = 0,
                             "Manual"=1),
                      gear = "Number of forward gears",
                      carb = "Number of carburetors"
)
# Different statistics for different variables.
mtcars %>%
    tab_cols(total(), vs) %>%
    tab_cells(mpg) %>% 
    tab_stat_mean() %>% 
    tab_stat_valid_n() %>% 
    tab_cells(am) %>%
    tab_stat_cpct(total_row_position = "none", label = "col %") %>%
    tab_stat_rpct(total_row_position = "none", label = "row %") %>%
    tab_stat_tpct(total_row_position = "none", label = "table %") %>%
    tab_pivot(stat_position = "inside_rows") 
```


### formattable
```{r}
library("formattable")
# Read CSV into R
MyData <- read.csv(file="C:/Users/daheekim/OneDrive - Ralco Nutrition, Inc/Rfile/Rpubs/Visualization/african_crises.csv", header=TRUE, sep=",")
mydata <- subset(MyData, MyData$year< 1870)
formattable(table(mydata$year, mydata$country))
```


### tidyr

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(formattable)
library(tidyr)
library(dplyr)
library(readxl)
texasdata <- read.csv("https://raw.githubusercontent.com/dana6691/R_project/master/Data/Imagine_Austin_Indicators.csv", header=TRUE, sep=",")

# select rows, columns, average by rows, percentage of change
i1 <- texasdata %>%
  filter(`Indicator.Name` %in% 
           c('Prevalence of Obesity', 'Prevalence of Tobacco Use', 
             'Prevalence of Cardiovascular Disease', 'Prevalence of Diabetes')) %>%
  select(c(`Indicator.Name`, `X2011`, `X2012`, `X2013`, `X2014`, `X2015`, `X2016`)) %>%
  mutate (Average = round(rowMeans(
    cbind(`X2011`, `X2012`, `X2013`, `X2014`, `X2015`, `X2016`), na.rm=T),2), 
    `Improvement` = round((`X2016`-`X2011`)/`X2011`*100,2))
i1
formattable(i1)
```



### stargazer
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
**stargazer**(  ..., 
            type = "latex", title = "", style = "default", 
            summary = NULL, out = NULL, out.header = FALSE,
            column.labels = NULL, column.separate = NULL,
            covariate.labels = NULL, dep.var.caption = NULL,
            dep.var.labels = NULL, dep.var.labels.include = TRUE,
            align = FALSE, 
            coef = NULL, se = NULL, t = NULL, p = NULL,
            t.auto = TRUE, p.auto = TRUE,
            ci = FALSE, ci.custom = NULL,
            ci.level = 0.95, ci.separator = NULL,
            add.lines = NULL, 
            apply.coef = NULL, apply.se = NULL, 
            summary.logical = TRUE, summary.stat = NULL,
            nobs = TRUE, mean.sd = TRUE, min.max = TRUE, 
            median = FALSE, iqr = FALSE )
</div>
--------------------------------------------------------------------------------------------
<div class = "blue">
* Type: "text", "html"
* ci: TRUE/FALSE
* ci.level: 0.8, 0.9
* omit.stat: =c("f", "ser")
</div>
```{r mylatextable, results = "asis"}
library(stargazer)
f1 <- lm(mpg ~ wt, mtcars) #2 OLS models
f2 <- lm(mpg ~ wt + hp, mtcars)
f3 <- lm(mpg ~ wt + hp + cyl, mtcars)
stargazer(f1, f2, f3, type = 'html')

```

```{r results = 'asis', warning=FALSE, message=FALSE}
library(stargazer)
f1 <- lm(mpg ~ wt, mtcars) #2 OLS models
f2 <- lm(mpg ~ wt + hp, mtcars)
f3 <- lm(mpg ~ wt + hp + cyl, mtcars)
stargazer(f1, f2, f3, type = 'html')

correlation.matrix <- cor(mtcars) #correlation matrix
stargazer(correlation.matrix, type="html")
```




