---
title: "R Notebook"
output: html_notebook
---

**Multivariate GAMs(Generalized Additive Model)**

generalized linear model in which the linear response variable depends linearly on unknown smooth functions of some predictor variables, and interest focuses on inference about these smooth functions.

```{r}
library(mgcv)
library(gamair)

# Examine the data
data(mpg)
head(mpg)
str(mpg)

# Fit the model with  sum of smooth functions and categorical variables
mod_city <-  gam(city.mpg ~ s(weight) + s(length) + s(price) + fuel + drive + style, 
                 data = mpg, method = "REML")

# Plot the model
plot(mod_city, pages = 1)
# Plot the results
plot(mod_city, residuals = TRUE, pch = 1, pages = 1)
```

## 50 basis functions and a smoothing parameter of 0.0001.
```{r}
# Fit the GAM
gam_mod_sk <- gam(accel ~ s(times,k=50), sp=0.0001, data=mcycle)
?gam
gam_mod_sk <- gam(city.mpg ~ s(weight,k=50) + s(length,k=50) + s(price,k=50) + fuel + drive + style, sp=0.0001, 
                 data = mpg)

# Visualize the model
plot(gam_mod_sk, residuals = TRUE, pch = 1)
```
```

```{r}
gam_mod_sk <- gam(accel ~ s(times,k=50), sp=0.0001, data=mcycle)
# Visualize the model
plot(gam_mod_sk, residuals = TRUE, pch = 1)
```

```{r}

```

# Category-level smooths for different auto types
```{r}
# Fit the model
mod_city3 <- gam(city.mpg ~ s(weight,by=drive) + s(length,by=drive) + s(price,by=drive) +drive,
                 data = mpg, method = "REML")

# Plot the model
plot(mod_city3, pages = 1)
```

